\subsection{Evaluation Criteria}
\label{subsec:evaluationCriteraCohen}
%Denne er kopiert men skal skrives om:
%This section is dedicated to the issue of evaluating the implementation and this project as a whole. Evaluation is an issue much discussed in the field of artificial intelligence(AI). Cohen and Howe claims many papers do an inadequate job of evaluating the result of their AI systems. The systems described in question in this thesis have an inherent black-box nature. This means it is inconceivable to understand the rationale behind why the system delivers its result. his complicates the evaluation. An evaluation with clear relative benchmarks is thus important and to avoid any pitfalls that invalidate the results. Examples of this are overfitting or data leakage. In this effort Cohen and Howe’s five stage process is used for evaluating empirical AI systems.

(Evaluating the implementation and this project as a whole.)
As initiated in Section\vref{sec:structuredLiteratureReview}, \citet{cohen88} introduced a five-stage model for evaluating research in terms of a five-stage cycle. This development process should be run as iterative cycles, and is begun answered in \vref{sec:structuredLiteratureReview} and \vref{sec:problemStatement}.
\begin{enumerate}
\item a topic is refined to a task and a view of how to accomplish the task
\item the view is refined to a specific method
\item a program is developed to implement the method
\item experiments are designed to test the program
\item the experiments are run
\end{enumerate} 

This thesis, two parts, the first is the structured literature review with related work Chapter 3, and an implementation with experiments Chapter 4 and 5. 

The task is to .., And the goal is to .... The hypothesis is that.. Implemented the program to test the method, and run experiments to evaluate against performance criteria.

\textbf{How is your reformulation an improvement?}
Has it been studied before. Kort oppsummering av Related Work 

\textbf{Is the research representative of a class of tasks?}

\textbf{Have any aspects been abstracted away?}
Estimates of travel demand.

\textbf{When have you successfully demonstrated a solution?}
Mandl's benchmark problem, performance criteria.