\section{Experimental Results}

Results should be clearly displayed and should provide a suitable representation of your results for the points you wish to make. Graphs should be labeled in a legible font and if more than one result is displayed on the same graph then these should be clearly marked.   Please choose carefully rather than presenting every results. Too much information is hard to read and often hides the key information you wish to present. Make use of statistical methods when presenting results, where possible to strengthen the results.  Further, the format of the presentation of results should be chosen based on what issues in the results you wish to highlight. You may wish to present a subset in the experimental section and provide additional results in the appendix.

\subsection{Structured Literature Review}
Duplicate literature, book of chapters, book of abstracts, book of references, literature not written in english, books, and literature with clearly irrelevant titles (for example literature from different research areas) were first removed based on the title. After that, relevant literature were filtered based on the abstracts. There were relatively many sources to the related literature after the initial filtering (367), and therefore we decided that we wanted the abstracts (or the keyword section) to explicitly mention swarm intelligence or algorithms associated with swarm intelligence, while it also described a problem connected to vehicle routing. For our literature review we decided to use the inclusion criteria solely on the title, abstract and keywords. After the inclusion criteria filtering, we had 42 sources for the related literature, including scientific papers and master theses. Table \ref{table:literature} on page \pageref{table:literature} shows the papers that were selected based on the inclusion criteria, and scored according to the quality criteria. When selecting the final literature we decided to do this solely based on the quality criteria scores. The average score of the read literature was 13.01 $\approx$ 13, and literature given a score $\geq{1.5}$ above average were selected. After this sorting we ended up with 14 final literatures. These 12 literatures are going to create the foundation of our thesis. Table \ref{table:finalliterature} on page \pageref{table:finalliterature} shows the final selected literature. The conducted process is entirely explained in appendix \ref{appendixA} and \ref{appendixB}.

\subsection{Stage 1 - Parameter Settings}

\begin{table}[H]
\centering
    \begin{tabular}{|l|l|l|l|l||l|l|l|l|l|}

 	\hline
 	1 & 2 & 3 & 4 & 5 & $d_0$ & $d_1$ & $d_2$ & $d_{unsat}$ & ATT \\
 	\hline
    ~ & ~ & ~ & ~ & ~ & ~ & ~ & ~ & ~ & ~ \\

	\hline
    \end{tabular}
    \caption {Parameter settings avg}
    \label{table:parameterSettings}

\end{table}

\subsection{Stage 2 - Performance Comparison}

Mandl as mentioned. llalala

\subsection{Stage 3 -  Scalability Experiments}
Time and Space Complexity