\section{Experimental Results}
\label{sec:expResults}
%Results should be clearly displayed and should provide a suitable representation of your results for the points you wish to make. Graphs should be labeled in a legible font and if more than one result is displayed on the same graph then these should be clearly marked.   Please choose carefully rather than presenting every results. Too much information is hard to read and often hides the key information you wish to present. Make use of statistical methods when presenting results, where possible to strengthen the results.  Further, the format of the presentation of results should be chosen based on what issues in the results you wish to highlight. You may wish to present a subset in the experimental section and provide additional results in the appendix.

\subsection{Parameter Settings}
\label{subsec:parameterSettings_results}

Table \vref{table:parameterSettings2} shows the parameters tested, their candidate values and the selected value. The complete experimental steps with the corresponding results can be found in, Appendix \ref{appendixC}, Table \vref{table:pm1} and Table \vref{table:pm2}. 
    \begin{table}[H]
    \centering
    \begin{tabular}{|c|c||c|}
    \hline
    Parameters & Candidate values & Selected value\\
    \hline
    $s$ & 10, 25, 50, 100, 150 & 50$^*$ \\
    $i$ & 1, 10 , 50, 100, 125 & 100$^*$ \\
    $E$ & 1\%, 10\%, 25\% 50\%, 75\%, 90\%, 99\% & 50\% \\
    $p_{b}$ & 0.0, 0.1, 0.3, 0.5, 0.7, 0.9 & 0.9 \\
    %$BR$ & 1\%, 10\%, 25\% 50\%, 75\%, 90\%, 99\% & 25\% \\
    $AF$ & 0\%, 1\%, 5\%, 10\%, 50\%, 75\%, 100\% & 25\% \\
    $CA$ & 0\%, 1\%, 5\%, 10\%, 50\%, 75\%, 100\% & 5\% \\
    \hline
    \end{tabular}
    \caption {Results from the parameter settings experiment}
    %The complete experimental steps with the corresponding results can be found in, Appendix \ref{appendixC}, Table \vref{table:pm1} and Table \vref{table:pm2}.
    \begin{itemize}[noitemsep]
    \item[$^*$:] \emph{\color{blue} Selected based on runtime}
    \end{itemize}
    \label{table:parameterSettings2}
    \end{table}

\textbf{Evaluation}
\newline
Based on the results shown i Appendix \ref{appendixC}, Table \vref{table:pm1} and Table \vref{table:pm2}, we observe that the stated Confidence Interval does not become remarkably better by running the algorithm 50 times compared to 30. This makes it reasonable to conclude that the results regarding the parameters that were ran 30 times are valid. 
\newline
%Because our confidence coefficient is sat to correspond to 95\%, we are able to say that we are 95\% confident that the true population parameter is between the lower and upper calculated values.

Observing the produced results of parameter $E$ in Table \vref{table:pm1}, evaporating 50\% of the pheromone each iteration gave the best average total fitness and the second best average travel time. Evaporating 75\% gave the best average travel time, and the second best total fitness, but according to the formula described in Section \vref{subsec:parameterSettings_setup} 50\% is selected. As one can observe, the best produced results is achieved by a candidate value greater or equal to 50\%. The algorithm seems to benefit from the fact that a great amount of pheromone evaporates each iteration. We believe this is because it compensates for some of the randomness the parameter $CA$ produces, by quickly removing pheromone from edges that were once used, but later discarded. One can also observe that the worst results were achieved when $E$ was sat to 99\%. Even though the algorithm benefits from a large percentage of evaporated pheromones, it reaches a threshold were the percentage becomes too big. By removing 99\% of the pheromone an edge that is usually used a lot, but for some reason not used as much the given iteration, it is ``punished'' too hard. 
\newline

The amount of $AF$ determines the amount of Following Ants ($FA$) in the next iteration, and the $FA$ follow the same path as the best ants' paths unconditionally. Observing the results obtained in Table \vref{table:pm2}, the $TOTFIT$ value deteriorates when the amount of $AF$ becomes greater than 25\%. When the amount of $FA$ becomes too great, a relatively large number of normal ants will not be able to explore new (possibly better) routes in the next iterations, and the algorithm may suffer from a local optima. But as one also can see, 25\% computes better results than the candidate values below. Rewarding some good route sets seems to boost the algorithms performance to some degree, and 25\% is selected as the final parameter for $AF$.

Based on the produced results, the selected value of parameter $p_b$ is 0.9. The value of $p_b$ is strongly dependent on the value of $AF$, because the more following ants, the more pheromone added to each edge in the best route sets. To ensure that rewarding more edges with the selected amount of pheromone did not negatively affect the algorithm's performance, the value of $p_b$ was tested with the new selected value of $AF$. As one can observe in Table \vref{table:pb_testing}, both $TOTFIT$ values have increased with the new increased value of $AF$, and the selected value for $p_b$ does not compute worse than when the $AF$ value was 10\%. The $ATT$ value increases after the new value of $p_b$, and the value of $p_b$ will be the same as it initial was selected. 

    \begin{table}[H]
    \centering
    \begin{tabular}{|c|c||c|c|}
    \hline
    $AF$ & $p_b$ & $ATT$ & $TOTFIT$\\
    \hline
    10\% & 0.5 & 11.302 & -269.279 \\
    10\% & 0.9 & 11.314 & -269.631 \\
    25\% & 0.5 & 11.366 & -272.392 \\
    25\% & 0.9 & 11.314 & -271.524 \\
    \hline
    \end{tabular}
    \caption {Testing the value of parameter $p_b$ to the parameter $AF$}
    \label{table:pb_testing}
    \end{table}




