\section{Related Work}
\label{sec:relatedWork}

Swarm intelligence algorithms has been proven to be useful in many vehicle routing problems, and many studies have been conducted to improve the solution, both regarding time complexity and quality. \citet{dorigo97} and \citet{lucic03} were two of the first published papers that shows methods from swarm intelligence being suitable for solving VRP's. They use respectively an ant colony system and a bee system to solve the Traveling Salesman Problem (TSP), which is a subproblem of VRP. 

Many computer scientists has since then studied the possibility of solving VRPs using swarm intelligence. \citet{hsiao04}, \citet{salehi-nezhad07}, \citet{tripathi09}, \citet{dias14}, and \citet{sedighpour14} all studied the possibility of using swarm intelligence to solve vehicle routing problems involving cars transporting either persons or goods. 

%Mangler informasjon om algoritmene som sammenlignes med. Parametersettingen er beskrevet, men ikke forklart. 
\citet{hsiao04} presented an approach to search for the best path of a map considering the traffic loading conditions. To do this, they proposed an ACO algorithm to search for the shortest path from a desired origin to a desired destination. The presented algorithm is a classic ACO algorithm without changes. To test their algorithm, the random-generated a map consisting of 100-500 nodes, and compared their algorithm to a brute method emphasizing on the time used to generate the route. Their results states that if the map consists of more than 200 nodes, the ACO performs better than a brute method. In fact, they found that the more nodes the map contains, the higher the benefit of using the ACO algorithm. 

\citet{salehi-nezhad07} presented an ant algorithm to search for the best path between two desired origin and destination intersections in cities, called Ant-based Vehicle Navigation algorithm. To get more accurate results than the classic ant algorithms they employed an \textit{awarding/punishment}-method, were the path found by the ``best ants'' are given more pheromone than the path of the ``bad ants''. In order to find the best path, the presented algorithm is concerned about the parameters \textit{distance}, \textit{width}, \textit{traffic load}, \textit{road risk}, \textit{road quality}, and \textit{number of intersections}. The importance of each of the parameters are weighted from 0 to 1 by the user. 

%Mangler informasjon om algoritmene som sammenlignes med
\citet{tripathi09} solved the vehicle routing problem with stochastic demand, in which the customer demand is modeled as a stochastic variable. They performed this using an improved version of the ACO approach, called ns-AAA SO. The proposed algorithm orients the search progressively towards favoring the global optimal solution. To do this they defines that a complete iteration consists of two tours: The first tour is a social tour that corresponds to a standard ACO iteration. The second tour is a neighborhood tour where the ants are allowed to communicate important information found in the social tour and change their solutions. If the fitness value of the new solution is better, the old solution found in the social tour is replaced. To favor the optimal solution, the path of the global best path is given more pheromones. Further, to prevent the search from entrapment into a local optima, a minimum quantity of pheromone on any edge, $t_{min}$, is always maintained. The performance of ns-AAA SO was compared with both a standard ACO algorithm and a genetic algorithm. They found that ns-AAA SO outperforms the other two algorithms in every problem instance described by the authors.

%Mandler informasjon om parametersetting
\citet{dias14} introduced an inverted ACO (IACO) algorithm. The idea is that the IACO algorithm inverts the logic of the classical ACO algorithm by converting the attraction of ants towards pheromones into a repulsion effect. The proposed approach was used in a decentralized traffic management system, where the drivers acted as the inverted ants. The drivers were repelled by the scent of pheromones (other drivers), and the system thus avoids congested roads. The described approach was compared to a shortest-time algorithm (ST), and the IACO algorithm performs better than the ST algorithm with the respect to trip time, travel length, fuel consumption and $CO_2$ emissions. This is as long as a considerable amount (25-50\%) of the vehicles uses the inverted ant algorithm to decide which road to choose. 

%Sammenligner ikke algoritmen mot original ACO, selvom de sier at de ønsker å forbedre ACO i introduksjonen
\citet{sedighpour14} introduced a hybrid ACO (HACO) algorithm to solve the open vehicle routing problem (OVRP). This is a sub problem of the classical VRP where the vehicles are not required to return to the depot. To overcome some of the shortcomings, such as slow computing speed and local convergence, of the original ACO algorithm they made three major improvements. First they equipped each node with a candidate list containing nodes nearby that had not yet been visited. Second, at each iteration, they applied several local search techniques to the \textit{n} best solutions found to improve them further. Third, they decided the amount of released pheromone based on the rank of the best known solution found so far. The HACO algorithm was compared with three versions of PSO (standard PSO, PSO without one-point move (PSOWO) and PSO without neighbors (PSOWN) regarding performance. The algorithms were tested on fifteen different sets, consisting of 19 to 72 nodes with 2 to 7 vehicles fixed at the minimum possible. Their result table shows that HACO performs better than the others regardless of the test case used.\newline

Urban Transit Network Design Problem (UTRP), a subproblem of VRP, considers other objectives and requires other methods for generating solutions than classical VRP problems. \citet{yang07}, \citet{salehinejad10}, \citet{jiang10}, \citet{poorzahedy11}, \citet{nikolic14}, and \citet{kechagiopoulos14} all addressed problems related to urban transit networks.

%Parameterne er nevnt og den sammenligner med relevante algoritmer
\citet{yang07} presented an optimization algorithm for a urban bus network design (UBND), based on \citet{dorigo96}s Ant Colony Algorithm (ACA), called coarse-grain parallel ant colony algorithm (CPACA). CPACA is very similar to the original ACA, but it applies less communication between the ants by dividing the colony of ants into sub colonies that runs in parallel and only communicate with each other. The research aims to minimize the average trip time by maximizing the number of direct travelers per unit length. Their results are compared with the classical MAX-MIN ant system (MMAS)\citep{stutzle99} and with ACA with Ant-weight strategy (ACA+). They found that CPACA performs best regarding both average direct traveler density and run time. 

%Parameterne er nevnt og den sammenligner med relevante algoritmer.
\citet{salehinejad10} introduced a route selection system which uses an ant colony system to detect an optimum multiparameter direction between two desired points in urban areas. Their algorithm is called Fuzzy Logic-Ant Colony System (FLACS), and like \citet{tripathi09} the pheromone updating is conducted in two parts. First the ants leave pheromone as they walk along a path (local pheromone update rule), and second the global best ant's path is given extra pheromone to favor the global best solution (global pheromone update rule). FLACS differs from other ACSs by the employment of fuzzy logic for the local pheromone updating. The system is concerned about the parameters ``Distance'', ``Traffic Flow'', and ``Incident Risk'' on each edge. The importance rate of each of these parameters are user determined. The edge's total amount of the mentioned parameters are the input to the fuzzy logic component, which then decides how much pheromone to be added to the selected edge. In addition FLACS also implements a tabu list, where visited nodes are added to avoid cycles. The algorithm is applied to a part of London, United Kingdom, consisting of 42 junctions. The FLACS algorithm is compared to a standard ACS-algorithm and a $A^*$-ACS-algorithm emphasizing on the parameters mentioned above. They found that FLACS performs better at average than both the standard ACS and the $A^*$-ACS regarding operational cost, regardless of the importance rate of the parameters. It is, however, worth mentioning that the estimation of further traffic data is done by ANNs, and therefore the traffic data used for each algorithm is not exactly the same.They found that FLACS has less running time than $A^*$-ACS, but more than the standard ACS due to its Fuzzy Logic system component. 

%Parameterne er nevnt, men ikke begrunnet. Sammenligner med relevante algoritmer. 
\citet{jiang10} describes an improved ACO (IACO) algorithm to solve the Urban Transit Network Optimization which is described as a typical nonlinear combinatorial optimization problem. The specific improvement made to the algorithm is the implementation of a stagnation counter to determine whether the algorithm has fallen into stagnation. When there is no better solution found after an iteration, the stagnation will increase by 1. When the stagnation counter reaches a certain threshold, the pheromone levels associated with each edge is reinitialized. This improvement is done to compensate for the classical ACOs shortcomings of easily falling into stagnation and therefore obtain a local optimal solution. The IACO algorithm is, like the algorithm described by \citet{yang07}, compared to the classical MMAS algorithm. The results shows significant improvement to the convergence speed compared to MMAS. The also found that ACO also performed better both regarding average number of iterations and average path distance. 

%Parameterne er nevnt, diskutert og begrunnet. Sammenligner for så vidt med relevante algoritme (GA).
\citet{poorzahedy11} proposed an Ant System application for solving the bus network design problem (BNDP). BNDP is defined in this research as the study of choosing a subset of interconnected bus routes among a given set of such routes. A successful solving of the BNDP minimizes the total travel time of the users of the network and the operators costs. Like the FLACS algorithm proposed by \citet{salehinejad10}, the proposed AS algorithm also employs a tabu list for each ant where visited nodes are added. Their solution generates multiple nests across the pedestrian network and each nest is responsible for creating a sub network, which is combined to a complete bus network at the end. The algorithm is only concerned about one objective; a combination of travel time for the users and the bus fleet size for the operator. The application was used to design the bus network of Mashhad to further be compared with a genetic algorithm (GA). Their results shows that their algorithm performs better than the GA in both the number of routes, fleet size, in-vehicle travel time and waiting time. GA performs better than the Ant System algorithm with respect to travelers walking time. The walking time attained by AS is 3 \% greater than the walking time attained by the GA. We believe this is because both the fleet size and number of routes are attained by AS is smaller than the ones obtained by GA. Both the GA and the AS performs significantly better than the existing solution on all measures.  

%Parameterne er nevnt, men ikke begrunnet. Sammenligner med relevante algoritmer. 
\citet{nikolic14} proposed a model for solving the transit network design problem. To do this they used an improved version of the original BCO \citep{lucic03} where the bees starts with an initial solution at each iteration and tries to improve this. This initial solution is the best known solution so far. They divided the network design problem in to two parts; in the first part the actual network is designed (decided which links to be included) and in the second part bus routes were created based on the designed network. The algorithm was tested on Mandl's benchmark problem of a Swiss bus network\citep{mandl80} and compared to competitive approaches (\citet{mandl80}; \citet{shih94}; \citet{baaj95}; \citet{bagloee11}) regarding total travel time, in-vehicle time, out-of-vehicle time, fleet size and number of transfers. The found that the proposed algorithm performed best regarding total travel time and number of transfers if the order of importance was set to favor what was best for passengers and the number of lines was greater than 4. If the order of importance was set to favor what was best for the operator, the algorithm created the solution with the smallest fleet size independent of number of lines, but then the algorithm performed mediocre regarding all the other measures. 

%Parameterne er nevnt, diskutert og begrunnet. Sammenligner med relevante algoritmer.
\citet{kechagiopoulos14} designed and presented an original PSO algorithm without any changes or improvements. Their goal was to find an efficient solution to the urban transit routing problem (UTRP), which is a NP-hard problem that deals with the construction of route networks for public transportation. The target problem was, like \citet{nikolic14}, Mandl's benchmark problem, and their algorithm was compared with competitive approaches, including genetic algorithms and other metaheuristic approaches mentioned in literature (\citet{baaj91}; \citet{chakroborty02}; \citet{kidwai98}; \citet{fan10}; \citet{fan09-2}; \citet{zhang10}; \citet{chew12}). The algorithms were compared with regard to the percentage of total transfer demands satisfied directly ($d_0$), with one transfer ($d_1$), two transfers ($d_2$), or with more than two transfers or not satisfied at all ($d_{unsat}$). The algorithms are also compared regarding average in-vehicle travel time ($ATT$). The experiments are conducted on route set designs with four, six, seven and eight routes. They found that the proposed algorithm performs better than the competitors regarding $ATT$ independent the route size, and achieves a better percentage of direct travelers ($d_0$) except when the route size is four.  \newline

Using methods from swarm intelligence to solve VRP's are still fairly unexplored, and there are many questions to be both asked and answered. However, in the passed decade, there has been published a fare amount of research on the subject, and we believe that research which clearly compares the proposed SI-algorithm to other relevant algorithms increases the credibility of the research and also contributes valuable information to the field. We see that a lot of the newest published research addresses the weaknesses of classical SI-methods and makes changes to the original algorithms to overcome some of these. In these cases we believe that the conducted experiments should include comparison with other swarm inspired methods to indicate whether or not their solution improved the addressed weaknesses. 

\citet{tripathi09}, \citet{yang07}, \citet{salehinejad10}, and \citet{jiang10} all presented research where their swarm inspired algorithm was designed to overcome some of the known weaknesses, such as getting stuck at local optima. They compared their solutions with other corresponding swarm methods, achieving promising results. Because of this comparison, they are able to concretely say whether or not the addressed weaknesses are improved. 

\citet{hsiao04} and \citet{sedighpour14} created ACO inspired algorithms, and they also wanted to overcome some of the known weaknesses of ACO. \citet{hsiao04} stated in the introduction that their method differs from other ACO methods because ``it can be implemented easily, it is flexible for many different problems' formulation, and the most of all, it can escape the local optima of the given problem''. However, neither \citet{hsiao04} nor \citet{sedighpour14} compared their proposed algorithms to other implementations of ACO. Because of this we believe their research are not able to conclude whether or not it actually overcomes some of ACO's weaknesses. \citet{hsiao04}'s algorithm is in fact only tested against against a brute method which is not described in the research other than in the result table. Neither \citet{dias14} nor \citet{poorzahedy11} tests their solution against other swarm intelligence methods, but against other reasonable algorithms, respectively a Shortest Time-algorithm and a GA. In \citet{dias14}'s research we believe that it makes sense to only test against an ST-algorithm, because they have inverted a core factor of the original ACO algorithm. An comparison to, for example, the original ACO would not only be non-descriptive, but possibly not feasible. We also believe that the comparison against a GA in the research of \citet{poorzahedy11} is descriptive, because they did not add additional features to the AS algorithm.\citet{salehi-nezhad07} did not compare their algorithm against any other algorithm at all, which makes their results hard to verify. \newline

The performance of metaheuristic methods, including swarm inspired methods, are highly dependent on their parameter settings. We believe the process of parameter tuning is an important contribution to the field of swarm intelligence in general, because multiple of the researches, including \citet{salehi-nezhad07} and \citet{yang07}, describes their parameter setting as a product of ``trial and error''. \citet{sedighpour14}, \citet{poorzahedy11}, and \citet{kechagiopoulos14} discussed and justified their parameter settings by conducting their experiments in two parts; one for parameter setting and one for performance. \citet{hsiao04}, \citet{salehi-nezhad07}, \citet{tripathi09}, \citet{sedighpour14}, \citet{yang07}, \citet{salehinejad10}, \citet{jiang10}, \citet{poorzahedy11}, \citet{nikolic14}, and \citet{kechagiopoulos14} all describes the parameters used by their algorithm. This makes their experiments feasible to replicate and compare against. The research of \citet{dias14} lacks information about parameter settings all together. We consider this to be a weakness of their research, and therefore not feasible to replicate and compare with. \newline

The size of the test cases used are an important factor for determining both scalability and robustness of the proposed algorithm. \citet{nikolic14} and \citet{kechagiopoulos14} both uses Mandl's benchmark problem as input. This benchmark problem is a small network containing 15 nodes and 21 edges.  Mandl's network is widely used and acknowledged by multiple researchers, including \citet{baaj91}, \citet{chakroborty02}, and \citet{fan09}. We believe this is a strength of their researches, because this enables them to compare their results to a numerous of other solutions using the same benchmark problem. However, as mentioned, the Mandl network is quite small. We believe that the robustness of their algorithms regarding both time and space complexity could have been verified by also applying their algorithm to a larger test case.\citet{salehi-nezhad07} also applied their solution to a small test set, containing only 27 intersections and requiring only 5 ants and, like the authors that used the Mandl Network, we believe the robustness could have been verified by also applying the algorithm to a larger test set.  \newline

%Regarding our research question \ref{itm:1a}, we conclude after this literature review that swarm intelligence methods are suitable for solving vehicle routing problems.
After a structured review of the related work we can conclude that swarm intelligence methods are suitable for solving vehicle routing problems, and with this answer our research question \vref{itm:1a}.
\citet{tripathi09}, \citet{dias14}, \citet{poorzahedy11}, \citet{nikolic14}, and \citet{kechagiopoulos14} all compared their algorithm against other approaches than SI and found that the proposed SI-algorithms generally performed better. It seems that the state-of-the-art of solving vehicle routing problems using swarm intelligence methods (research question \vref{itm:1b}) can be summed up to as being inspired by the original SI-algorithms, but to add and remove features to make the algorithm more suited for the tasks. With respect to research question \vref{itm:1c}, ten out of the twelve reviewed papers made changes to the original algorithm and the specific changes are described above. We notice a trend of implementing a notion of the best known solution so far, and using this to either directly or indirectly improve the solutions created by the individuals of the swarm (\citet{tripathi09}; \citet{sedighpour14}; \citet{nikolic14}). The original PSO algorithm already utilize the use of the best known solution so far, and the implementation of this in ACO and BCO approaches is, to the best of our knowledge, the only attempt to combine different SI methods (research question \vref{itm:1d}). 