\section{System assessments}
The aim of designing a route network is to optimize specific criteria that define its efficiency and quality. Also, some real world constraints should be satisfied. The evaluation criteria and constraints used by the proposed system are inspired by \citep{kechagiopoulos14}.

\subsection{Constraints}
\label{sec:algoConstraints}
During the route set generation, described in Section \vref{sec:algoCreatingRouteSet}, the system's constraints are the following: 
\begin{enumerate}
\item \label{itm:constraintCycles} \textbf{No cycles (or backtracks) in the graph is allowed.} In other words, a node visited once in a route should not be visited again in the same route. 
This corresponds to the real world constraint that a bus route should only include a given bus stop once. 
\item \label{itm:constraintRouteSize} \textbf{The route size is predefined. The routes shall not exceed the maximum or attain the minimum limit of nodes.}
This corresponds to the real world constraint saying that a bus route should include at least a number $n$ bus stops, and must not exceed a number $m$ of bus stops. This number is usually sat by the bus service provider based the size of the transit network and cost limitations. 
\item \label{itm:constraintRouteSetSize} \textbf{The route set size is predefined.}
This corresponds to the real world constraint that a service provider must be able to determine the number of bus routes in the transit network. This number is, like Constraint \ref{itm:constraintRouteSize}, sat based on the size of the transit network and cost limitations. 
\item \label{itm:criteriaConnectedGraph} \textbf{The created route sets must correspond to a connected graph.}
This corresponds to the real world constraint saying that a passenger must be able to travel between any two bus stops in the transit network. 
\end{enumerate}

\subsection{Evaluation criteria} 
This evaluation of the ant's performance is done after each route set generation and is based on the following criteria:
\begin{enumerate}
\item \label{itm:criteriaTotalTravelTime} The sum of the difference between the total travel time experienced by each passenger and the travel time of the shortest possible path, referred to as $F_1(r)$.
\item \label{itm:f2} A score which reflects the percentage of passengers traveling either directly, transferring once or transferring twice, referred to as $F_2(r)$.
\item A score which reflects the percentage of passengers transferring more than twice, referred to as $F_3(r)$. 
\end{enumerate}
These evaluation criteria are used to calculate the Total Fitness, $TOTFIT$, of route set $r$, which process is described in Section \vref{sec:totfit}.



