\section{SuperSwarm Optimization}
\label{section:methodDescription}

The baseline of the proposed algorithm, SuperSwarm Optimization (SSO), is an implementation of the ACO algorithm introduced by \citet{nanda11}, described in chapter \vref{backgroundAndMotivation}. As initiated in Section \vref{sec:problemStatement}, will the some acknowledged attributes inspired by PSO and BCO, be added to the ACO algorithm aiming to overcome some of ACO's known limitations and to boost the algorithm's performance. The ants generated ants will also be given``memory'', in order to recall whether a node is visited in an earlier route within the same route set. This attribute is not linked to any optimization method from swarm intelligence, but is added because we observed that by given the ants memory they were more capable of creating route sets that together corresponded to a connected graph and by so fulfilled Constraint \vref{itm:criteriaConnectedGraph}. 

One of the supplementary attributes added is \textit{Inertia Weight} from PSO. Inertia Weight is a decreasing parameter brought to PSO for balancing local and global search. As illustrated in Figure \vref{fig:psoBeginning} and Figure \vref{fig:psoEnd}, the particle in PSO tends to explore more in early iterations, and becoming more organized and coordinated in the later iterations of the algorithm. In the initialization phase of SSO, an an amount of the generated ants will be declared ``crazy''. A so called \textit{Crazy Ant}, will work randomly, and not consider edge values when selecting nodes to be included in a route. The probability of an ant being declared crazy is given by a predefined start value (CA), decreasing iteratively with the inertia weight (IW). The Crazy Ants are implemented in order to compensate for the original ACO algorithm's weakness of frequently getting stuck at a local optimum. %The IW value, as in PSO, is high in the early iterations, denoting a higher amount of CA, and decreases in pace with the IW. 
 %The probability that ant $a$ is declared crazy will never reach zero, so there always is a probability that $a$ is declared crazy.
Further, the individual's awareness of the global best solution from PSO is added. Each individual particle in PSO knows the best position achieved among all the particles so far. To implement this feature to SSO, the route set of the global best ant is retained and updated if an ant performs better than the current best ant. If an edge is included in the route set of the global best ant, this increases the probability that this edge will be chosen by other ants. 
 %CA combined with the inertia weight is inspired by the way the inertia weight in PSO favors exploration in early iterations and exploitation in the later.

Finally, the \textit{following} attribute from BCO is added. As explained in \vref{subsec:BCO}, deciding which bee to follow is in BCO considered to be a function of the quality of the food source to the recruiter. After the algorithm's first iteration will an amount, $n$, of the generated ants be initialized as ``followers'', also referred to as Following Ants (FA). The FA's will follow the $n$ best ants from the previous generation unconditionally. The Following Ants and the awareness of the global best solution is implemented in order to boost the algorithm's performance, by favoring good solutions.

%What we hope to achieve with these features is overcoming the ACO limitation of getting stuck at a local optima, as well achieving better results concerning the Performance Criteria, introduced in Section \vref{sec:performanceCriteria}.

%%Artifacts:
%\begin{enumerate}
%\item The ants have memory. It can remember whether or not it has visited a node in the creation of the route set.
%\item The ants have a notion of the global best ant. The ant will favor the edge chosen by the global best ant. (PSO)
%\item The ants can be ``crazy''. A crazy ant chooses next nodes at random given possible nodes, not considering the edge %values. This is to compensate for ACO getting stuck at local optima.
%\item An inertia weight is used. The inertia weight is used to calculate the number of crazy ants. At the beginning the number of crazy ants is larger (exploring). The inertia weight is decreased by each iteration, and therefore the number of crazy ants is decreased (exploiting). PSO.  \emph{\color{red} Check if inertia weight is mentioned in the PSO-section. If not write about it and refer to http://www.softcomputing.net/nabic11_7.pdf}
%\item After the first run, some ants are initialized as ``uncommitted followers''. They follow the $n$ best ants from the previous iteration without doubt. (BCO)
%\end{enumerate}



